
\cvsection{Work Experience}
\begin{cventries}
\cventry
{Lead Data Scientist} % Job title
{Earnest} % Organization
{San Francisco, California} % Location
{Jan. 2019 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Core data scientist on the team building machine learning services that support Earnest underwriting infrastructure.}
\item {Developed a Python microservice template. This template allows a person on the team to easily build and deploy Python microservices. It comes with ORM, logging, dependency management, and a variety of automation utilities that enable rapid model deployment.}
\item {Researched, built and deployed an income service model. This model outperformed several 3rd party top tier providers and supports 50\% automation in underwriter decision making.}
\item {Researched and built a customer acquisition model that led to a 40\% reduction in direct mail marketing costs and outperformed several third-party providers, such as Epic and LendingScience.}
\item {Supervised the work of 3-4 direct reports (mix of Data Engineers and SWE) by scoping out project requirements, performing sprint reviews, retrospectives, postmortems, code reviews, handling promotions and individual mentoring.}
\item {Exposed data from over a dozen microservices in Redshift. Set up the tone for data governance and data documentation. Maintained and optimized the data warehouse.}
\item {Wrote a Python microservice that supports dynamic pricing and scoring. The service is responsible for scoring \$10 billion of student loan volume/year.}
\end{cvitems}
}

\cventry
{Senior Data Scientist} % Job title
{} % Organization
{} % Location
{Jul 2017 - Jan. 2019}
 % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Managed Looker administration, maintenance, and optimization.}
\item {Standardized the process of developing models internally by writing a python package (earnest-ml) which allowed Data Scientists and Engineers to develop models using reproducible workflows.}
\item {Wrote an artifact pipeline that allowed the team to have parity between feature transformation done during training and inference. This cut down model deployment time by 70\%.}
\item {Developed and productionalized a personal scoring model that led to a 40\% increase in the number of approved applications with a negligible increase in default risk.}
\end{cvitems}
}

\cventry
{Data Scientist} % Job title
{} % Organization
{} % Location
{Jul 2016 - Jul 2017}
 % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Refactored existing risk scoring models in R and Scala.}
\item {Built a hierarchy of conversion models that guided user flow through our conversion funnel.}
\end{cvitems}
}

\end{cventries}